Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-06-26 paper.tex
Add County Mayo image

Area-based approaches were developed before network-based tools, such as
a 2007 regression-based model to estimate the percentage of cycling
trips to work in England and Wales based on socioeconomic,
transportation, and physical factors at the small area (wards) level in
2007 \citep{parkin_estimation_2007}. They found that areas with a higher
percentage of females, non-whites, car ownership, lower socioeconomic
classes, income, distance to work, population density, poor highway
conditions, hills, rainfall, and fewer off-road bicycle routes tended to
have a lower proportion of cycling to work. The approach also generated
``forecasts for potential levels of bicycle use'' with increases in
off-road routes, improvements of highway and, conversely, increases in
car ownership and distance to work leading to decreases in cycling to
work.

@@

>>>>

Area-based approaches were developed before network-based tools, such as
a 2007 regression-based model to estimate the percentage of cycling
trips to work in England and Wales based on socioeconomic,
transportation, and physical factors at the small area (wards) level in
2007 \citep{parkin_estimation_2007}. They found that areas with a higher
percentage of females, non-whites, car ownership, lower socioeconomic
classes, income, distance to work, population density, poor highway
conditions, hills, rainfall, and fewer off-road bicycle routes tended to
have a lower proportion of cycling to work. The approach also generated
``forecasts for potential levels of bicycle use'' associated with
increasing in off-road routes and, conversely, increasing car ownership
levels and distances travelled to work leading to decreases in cycling.

@@

\includegraphics{paste-9.png}
